Ae. albopictus CPP manuscript

### 2020-04-30 Albopictus_cpp_MS.Rmd
Figure update

```{r maps, echo=FALSE, include=FALSE}
usa<-map_data("usa")
jp<-map_data("japan")
pops<-data.frame(read.csv("mapping_pops_cpp_expt.csv"))
us_map<-ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group=group), fill=NA, color="blue") + 
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="US"), aes(x = longitude, y = latitude), size = 1) + xlim(c(-85, -65)) +
  geom_label(data=filter(pops, country=="US"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines")) +
  theme_bw() 
japan_map<-ggplot() + geom_polygon(data = jp, aes(x=long, y = lat, group=group), fill=NA, color="red") + 
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="JP", only_2008=="n"), aes(x = longitude, y = latitude), size = 1)  + xlim(c(125, 147)) +
  geom_label_repel(data=filter(pops, country=="JP", only_2008=="n"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines")) +
  theme_bw() + theme(axis.title.x=element_blank(), axis.title.y=element_blank())

#bw locations map
us_map_bw<-ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group=group), fill=NA, color="dark gray") + 
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="US"), aes(x = longitude, y = latitude), size = 2, shape=21, color="black", fill="gray", stroke=1) + xlim(c(-87, -65)) + ylim(c(24,48)) +
  geom_text_repel(data=filter(pops, country=="US"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines"), nudge_x=1.5, size=4) + theme_bw() + theme(text=element_text(size=24), plot.margin = unit(c(0,0,0,0), "cm"), panel.grid=element_line(size=0.1)) + xlab("") + ylab("")

japan_map_bw<-ggplot() + geom_polygon(data = jp, aes(x=long, y = lat, group=group), fill=NA, color="dark gray") +
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="JP", only_2008=="n"), aes(x = longitude, y = latitude), size = 2)  + xlim(c(125, 147)) + ylim(c(24,48)) +
  geom_text_repel(data=filter(pops, country=="JP", only_2008=="n"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines"), size=4) + theme_bw() + theme(text=element_text(size=24), plot.margin = unit(c(0,0,0,0), "cm"), panel.grid=element_line(size=0.1)) + xlab("") + ylab("Latitude")

map_panels_bw<-plot_grid(japan_map_bw, us_map_bw)
```

@@

```{r, echo=FALSE, include=FALSE}
#FIG S4
gdd_deadline_plots<-ggplot(filter(gdd465_all, only_2008=="n", year!=2018), aes(x=latitude, y=gdd465, fill=country)) + scale_fill_manual(values=c("black", "gray"), name="Country") + geom_point(shape=21, size=3) + facet_wrap(~year) + xlab("Latitude") + ylab("GDD Deadline (ordinal day)") + theme_bw() + 
theme(legend.position="bottom", text=element_text(size=18)) 
```

@@

gdd_08 <- ggplot(filter(gdd465_all_new, year==2007, CPP_YEAR==2008), aes(x=gdd465, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=22) + stat_smooth(method=lm, se=FALSE, aes(color=country), linetype="longdash") + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.25,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    xlab("GDD Deadline 2007 (ordinal day)") + ylab("CPP (h), 2008") + ylim(12.3,14.2)

gdd_18 <- ggplot(filter(gdd465_all_new, year==2017, CPP_YEAR==2018), aes(x=gdd465, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=21) + stat_smooth(method=lm, se=FALSE, aes(color=country)) + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.25,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
xlab("GDD Deadline 2017 (ordinal day)") + ylab("CPP (h), 2018") + ylim(12.3, 14.2)

@@

```{r echo=FALSE, include=FALSE}
#FIG 4
gdd_cpp_plot<-plot_grid(gdd_08, gdd_18, gdd_cpp_interval_08, gdd_cpp_interval_18, nrow=2, labels="AUTO")

```{r echo=FALSE, warning=FALSE}
#FIG S5A
#black=Japan, gray=US / circle=2018, square=2008 / solid line=2018, dashed line=2008

@@

```{r}
#FIG S5
plot_grid(gdd_by_interval, pcas_for_fig, nrow=2, labels="AUTO")
```

>>>>

```{r maps, echo=FALSE, include=FALSE}
usa<-map_data("usa")
jp<-map_data("world") %>% filter(region=="Japan")
pops<-data.frame(read.csv("mapping_pops_cpp_expt.csv"))
us_map<-ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group=group), fill=NA, color="blue") + 
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="US"), aes(x = longitude, y = latitude), size = 1) + xlim(c(-85, -65)) +
  geom_label(data=filter(pops, country=="US"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines")) +
  theme_bw() 
japan_map<-ggplot() + geom_polygon(data = jp, aes(x=long, y = lat, group=group), fill=NA, color="red") + 
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="JP", only_2008=="n"), aes(x = longitude, y = latitude), size = 1)  + xlim(c(125, 147)) +
  geom_label_repel(data=filter(pops, country=="JP", only_2008=="n"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines")) +
  theme_bw() + theme(axis.title.x=element_blank(), axis.title.y=element_blank())

#bw locations map
us_map_bw<-ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group=group), fill=NA, color="dark gray") + 
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="US"), aes(x = longitude, y = latitude), size = 2, shape=21, color="black", fill="gray", stroke=1) + xlim(c(-87, -65)) + ylim(c(24,48)) +
  geom_text_repel(data=filter(pops, country=="US"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines"), nudge_x=1.5, size=6) + theme_bw() + theme(text=element_text(size=24), plot.margin = unit(c(0,0,0,0), "cm"), panel.grid=element_line(size=0.1)) + xlab("") + ylab("")

japan_map_bw<-ggplot() + geom_polygon(data = jp, aes(x=long, y = lat, group=group), fill=NA, color="dark gray") +
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="JP", only_2008=="n"), aes(x = longitude, y = latitude), size = 2)  + xlim(c(125, 147)) + ylim(c(24,48)) +
  geom_text_repel(data=filter(pops, country=="JP", only_2008=="n"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines"), size=6) + theme_bw() + theme(text=element_text(size=24), plot.margin = unit(c(0,0,0,0), "cm"), panel.grid=element_line(size=0.1)) + xlab("") + ylab("Latitude") + 
  labs(x = NULL)
map_panels_bw<-plot_grid(japan_map_bw, us_map_bw, align="hv")
```

@@

```{r, echo=FALSE, include=FALSE}
#FIG S4
gdd_deadline_plots<-ggplot(filter(gdd465_all, only_2008=="n", year!=2018), aes(x=latitude, y=gdd465, fill=country)) + scale_fill_manual(values=c("black", "gray"), name="Country") + geom_point(shape=21, size=2) + facet_wrap(~year) + xlab("Latitude") + ylab("GDD Deadline (ordinal day)") + theme_bw() + 
theme(legend.position="bottom", text=element_text(size=18)) 
```

@@

gdd_08 <- ggplot(filter(gdd465_all_new, year==2007, CPP_YEAR==2008), aes(x=gdd465, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=22) + stat_smooth(method=lm, se=FALSE, aes(color=country), linetype="longdash") + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.25,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    xlab("GDD Deadline 2007 \n(ordinal day)") + ylab("CPP (h), 2008") + ylim(12.3,14.2)

gdd_08_sameyear <- ggplot(filter(gdd465_all_new, year==2008, CPP_YEAR==2008), aes(x=gdd465, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=22) + stat_smooth(method=lm, se=FALSE, aes(color=country), linetype="longdash") + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.25,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    xlab("GDD Deadline 2008 \n(ordinal day)") + ylab("CPP (h), 2008") + ylim(12.3,14.2)

gdd_18 <- ggplot(filter(gdd465_all_new, year==2017, CPP_YEAR==2018), aes(x=gdd465, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=21) + stat_smooth(method=lm, se=FALSE, aes(color=country)) + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.25,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
xlab("GDD Deadline 2017 \n(ordinal day)") + ylab("CPP (h), 2018") + ylim(12.3, 14.2)

gdd_18_sameyear <- ggplot(filter(gdd465_all_new, year==2018, CPP_YEAR==2018), aes(x=gdd465, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=21) + stat_smooth(method=lm, se=FALSE, aes(color=country)) + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.25,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
xlab("GDD Deadline 2018 (ordinal day)") + ylab("CPP (h), 2018") + ylim(12.3, 14.2)

@@

```{r echo=FALSE, include=FALSE}
#FIG 4
gdd_cpp_plot_decade<-plot_grid(gdd_cpp_interval_08, gdd_cpp_interval_18, nrow=2, labels="AUTO")
#FIG S5
gdd_cpp_plot_year<-plot_grid(gdd_08, gdd_18, nrow=2, labels="AUTO")
```

```{r echo=FALSE, warning=FALSE}
#FIG S6A
#black=Japan, gray=US / circle=2018, square=2008 / solid line=2018, dashed line=2008

@@

```{r}
#FIG S6
plot_grid(gdd_by_interval, pcas_for_fig, nrow=2, labels="AUTO")
```
